---
title: "Lab 09 - Grading the professor, Pt. 1"
author: "Lindley Slipetz"
date: "03/30/2021"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE, warning = FALSE}
#install.packages("vctrs")
#install.packages("tibble")
#install.packages("tidyverse")
library(tidyverse) 
#install.packages("broom")
#install.packages("tidymodels")
#install.packages("ggplot2")
library(tidymodels)
library(openintro)
```

Okay, loading tidymodels ended up being kind of a nightmare, but now we're ready to go.

### Exercise 1

```{r score_bar}
ggplot(evals, aes(x=factor(score)))+
  geom_bar(stat="count", width=0.7, fill="black")+
  labs(x = "Score", y = "Count", title = "Distribution of teaching evaluation scores") +
  theme(axis.text.x = element_text(angle = 90))
```

```{r score_sum}
evals %>%
  summarise(averageRating = mean(score),
             sdRating = sd(score))
```

The distribution is positively skewed. Students tend to rate their courses highly. The average score is 4.17 with a standard deviation of 0.54. I'm actually a bit surprised by this, but I would explain it by my perception of the gender disparity in evaluations (of course, I'm going to evaluate that later, so maybe this will change). Men tend to get high scores and there's more male professors than female professors, so that would skew the distribution.

### Exercise 2

```{r scatter_1}
ggplot(evals, aes(x=score, y=bty_avg)) +
  geom_point() +
  labs(x = "Evaluation Score", y = "Beauty Score", title = "Evaluation score vs beauty score") 
```

While it does seem true that, generally, higher beauty score is associated with higher evaluations (because the higher beauty scores are associated with higher evaluations), it's not a strong
association. 

### Exercise 3

```{r jitter_1}
ggplot(evals, aes(x=score, y=bty_avg)) +
  geom_jitter() +
  labs(x = "Evaluation Score", y = "Beauty Score", title = "Evaluation score vs beauty score") 
```

Jitter makes it so the points aren't in straight lines. It makes it more clear that there might be a linear relationship between evaluation score and beauty score.

### Exercise 4

```{r linear_reg_1}
lm_model <- linear_reg() %>% 
            set_engine('lm') %>% 
            set_mode('regression')
lm_fit <- lm_model %>% 
          fit(score ~ bty_avg, data = evals)
lm_fit
```
**Regression model**: score = 0.6664bty_avg + 3.88034


###Exercise 5

```{r lin_reg_graph}
ggplot(evals, aes(x=score, y=bty_avg)) + 
  geom_jitter() +
  geom_smooth(method=lm, se=FALSE, color="orange") +
  labs(x = "Evaluation Score", y = "Beauty Score", title = "Evaluation score vs beauty score") 
```


### Exercise 6

A one unit change in score corresponds to a 0.6664 unit change in beauty score average.

### Exercise 7 

The mean of beauty score is 3.88034 when evaluation score is zero. I don't think this value is realistic in practice. I don't think someone would ever teach so bad as to get 0 from every student. 

### Exercise 8
```{r R_2}
glance(lm_fit$fit)
```
$R^2$ = 0.035, so the explains 3.5% of the variance of beauty average. It also tells us that the residuals are quite large.
