---
title: "Lab 09 - Grading the professor, Pt. 1"
author: "Lindley Slipetz"
date: "03/30/2021"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE, warning = FALSE}
#install.packages("vctrs")
#install.packages("tibble")
#install.packages("tidyverse")
library(tidyverse) 
#install.packages("broom")
#install.packages("tidymodels")
#install.packages("ggplot2")
library(tidymodels)
library(openintro)
```

Okay, loading tidymodels ended up being kind of a nightmare, but now we're ready to go.

### Exercise 1

```{r score_bar}
ggplot(evals, aes(x=factor(score)))+
  geom_bar(stat="count", width=0.7, fill="black")+
  labs(x = "Score", y = "Count", title = "Distribution of teaching evaluation scores") +
  theme(axis.text.x = element_text(angle = 90))
```

```{r score_sum}
evals %>%
  summarise(averageRating = mean(score),
             sdRating = sd(score))
```

The distribution is positively skewed. Students tend to rate their courses highly. The average score is 4.17 with a standard deviation of 0.54. I'm actually a bit surprised by this, but I would explain it by my perception of the gender disparity in evaluations (of course, I'm going to evaluate that later, so maybe this will change). Men tend to get high scores and there's more male professors than female professors, so that would skew the distribution.

### Exercise 2

```{r scatter_1}
ggplot(evals, aes(x=score, y=bty_avg)) +
  geom_point(size=2, shape=23) +
  labs(x = "Evaluation Score", y = "Beauty Score", title = "Evaluation score vs beauty score") 
```

While it does seem true that, generally, higher beauty score is associated with higher evaluations (because the higher beauty scores are associated with higher evaluations), it's not a strong association. 